%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REV023: Tue 30 Jan 2024 16:00
% START0: Thu 16 Aug 2018 22:00
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{TIPS}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{TIPS (1)}

\begin{itemize}

\item See also \url{https://rms46.vlsm.org/2/221.pdf}.

\item For any administrative issues, contact SEKRE at building B, $2^{nd}$ floor --
      especially for absences, illness, sick letters, follow-up exams, etc.
      Please do not contact the \textbf{Lecturer} (RMS).

\item Please complete the follow-up/paper work within six (6) working days (RMS).

\item Prepare the weekly MEMO as thoroughly as possible. 
      You should have mastered the material at the beginning of the week (RMS).

\item Study the Operating System Concept book, which deals with the material that
      will be discussed that week (MIM). Make a summary of the material in your Memo (IP).

\item You should understand every single problem of the past examinations.
      Write down all hints in your ''\textbf{MEMO}'' (MHP).

\item You are allowed to bring up to 6 sheets of MEMOs for the midterm (UTS) and
      up to 5 sheets of MEMOs for the final term (UAS) (RMS).

\item You should understand every single line of the ''\textbf{DEMOS}'' (MHP).

\end{itemize}

\end{frame}

% (10) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{TIPS (2)}

\begin{itemize}

\item You should ask \textbf{the lecturer} or anyone, anything you do not understand (TA).

\end{itemize}

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]
\frametitle{Special Thanks}

\begin{tabular}{|p{117mm}|}
\hline
\vspace{1mm}

\textbf{Special thanks} for writing and reviewing this material to: \\ [2mm]

\begin{tabular}{p{109mm}}
Anisha Inas Izdihar (AII),
Benedictus Alvin (BA),
Dennis Al Baihaqi Walangadi,
Dionisius Baskoro Samudra,
Eugene Brigita Lauw,
Ibnu Sofian Firdaus (ISF),
Irmanpen Panjaitan (IP),
Ivana Irene Thomas (IIT),
Marcia Nadin Pramasiwi,
Michael Giorgio Wirawan (MGW),
Muhamad Yoga Mahendra,
Muhammad Afkar (MA),
Muhammad Hanif Pratama (MHP),
Muhammad Iqbal Mahendra (MIM),
Muhammad Krishertanto Adityapu,
M. Ikhsan Kurniawan (MIK),
Nixi Sendya Putri (NSP),
Raihan Mahendra Sutanto (RM),
Rizki Leonardo (RL),
Shavira Adeva (SA),
Stefan Mayer Sianturi (SMS),
Thrisnadevany Amalia (TA),
Zhelia Alifa (ZA); \\ [2mm]
\end{tabular}
\\ [3mm]
\hline
\end{tabular}

\end{frame}

